### 2018-04-30 paper/intro.tex
up

In the following, in Section~\ref{system-model}, we introduce the
adversary model the desired privacy properties of \name. Section~\ref{design}
introduce the design of our proposed solution. Section~\ref{Performance}
evaluates the proposed approach. In Section~\ref{security-discussion}, we lead a security discussion
about advantages, shortcomings of our approach.
Finally, Section~\ref{conclusion} discusses future work and conclusions.
% Cashmere: resilient anonymous routing.
% Route fingerprinting in anonymous communications.
% Bridging and fingerprinting:
% Epistemic attacks on route selection
% Breaking the collusion detection mechanism of morphmix
% Denial of service or denial of security? How attacks
% on reliability can compromise anonymity

>>>>

In the following, in Section~\ref{system-model}, we introduce the
adversary model and the desired privacy properties of \name. Section~\ref{design}
introduces the design of our proposed solution. Section~\ref{Performance}
evaluates the proposed approach. In Section~\ref{security-discussion}, we lead a security discussion
about advantages, and shortcomings of our approach.
Finally, Section~\ref{conclusion} discusses future work and conclusions.
% Cashmere: resilient anonymous routing.
% Route fingerprinting in anonymous communications.
% Bridging and fingerprinting:
% Epistemic attacks on route selection
% Breaking the collusion detection mechanism of morphmix
% Denial of service or denial of security? How attacks
% on reliability can compromise anonymity
